\documentclass[letterpaper,12pt, oneside]{article}

\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\hypersetup{
	colorlinks = true,
	urlcolor = [rgb]{0.0,0.09,0.66}
}
\usepackage{etaremune}
\usepackage{upgreek}
\usepackage{textgreek}
\usepackage{textcomp}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

\usepackage{microtype}
\usepackage[version=4,arrows=pgf]{mhchem}

\usepackage{pifont}
\urlstyle{rm}
\usepackage{graphicx}
\graphicspath{ {images/}}

\usepackage[left=2.41cm, right=2.41cm, bottom=1.69cm, top=1.69cm]{geometry}

\usepackage{enumitem}
\setlist[itemize,enumerate]{align=parleft,left=0pt..1em,topsep=0.35em,itemsep=0.5em,parsep=0pt,partopsep=0pt}

\newcommand*{\Skype}{\href{skype:john.smith?add}{john.smith}}
\newcommand{\Absender}[1][\normalsize]{\Skype}

\pagenumbering{arabic}
\setlength{\parindent}{0pt}

% ---- central spacing controls ----
\newlength{\cvSectionBefore}
\newlength{\cvSectionAfter}
\newlength{\cvSectionToTable}
\newlength{\cvHeaderRuleGap}
\newlength{\cvHeaderTableBottomGap}
\setlength{\cvSectionBefore}{0.75em}
\setlength{\cvSectionAfter}{0.30em}
\setlength{\cvSectionToTable}{0.28em}
\setlength{\cvHeaderRuleGap}{0.30em}
\setlength{\cvHeaderTableBottomGap}{0.35em}

\newcommand{\cvsection}[1]{\par\vspace{\cvSectionBefore}{\Large\textbf{#1}}\par\vspace{\cvSectionAfter}}

\begin{document}

\begin{center}
\LARGE{Matthias \textbf{Raphael Stock}} \\
\normalsize{{Postdoctoral researcher}}

\end{center}
\vspace{-2.2ex}
\hrulefill

\normalsize

\vspace{\cvHeaderRuleGap}
\begin{center}
\begin{tabular}{l l l}
\href{https://manoa.hawaii.edu/}{University of Hawai'i at Mānoa} & \hspace{0.25in} & \href{mailto:rstock9@hawaii.edu}{rstock9@hawaii.edu} \\
\href{https://www.phys.hawaii.edu/}{Department of Physics and Astronomy} & \hspace{0.25in} & \\
\href{https://www.openstreetmap.org/?#map=19/21.298379/-157.816177}{2505 Correa Road, Watanabe 312, Honolulu, Hawaii 96822, USA} & & \\
 \end{tabular}
\end{center}

\vspace{\cvHeaderTableBottomGap}

\cvsection{Research Interests}
Light calibration systems for neutrino and dark matter experiments, organic and water-based liquid scintillator development and characterization, instrumentation, neutrino physics, solar neutrinos, neutrino astronomy, active galactic nuclei
\vspace{1em}\par
\cvsection{Employment}\vspace{\cvSectionToTable}
\begin{tabular}{@{} l p{13cm}}

		02/2026 – today & \textbf{Postdoctoral researcher} \\
		& University of Hawai`i at Mānoa, {USA} \\
		& Department of Physics and Astronomy \vspace{0.22em} \\

		11/2018 – 03/2025 & \textbf{Research and teaching assistant} \\
		& {Technical University of Munich, {Germany}} \\
		& TUM School of Natural Sciences, Department of Physics \\
		& Chair for Experimental Physics and  Astroparticle Physics (E15) \vspace{0.22em} \\

		06/2018 – 09/2018 & \textbf{Research assistant}\\
		& {Max Planck Institute for Extraterrestrial Physics (MPE)}, {Germany}  \\
		& Infrared/Submillimeter Group
	\end{tabular}
\vspace{0.5em}\par
\cvsection{Education}\vspace{\cvSectionToTable}
\vspace{0.5em}
\begin{tabular}{@{} l p{13cm}}
05/2019 – 07/2025 & \textbf{Dr. rer. nat. (PhD equivalent) in Physics} \\
                  & Technische Universit\"at M\"unchen (TUM), Germany \\
                  & Thesis:
                  \href{https://mediatum.ub.tum.de/?id=1782355}{\textit{“Development and Characterization of Novel Liquid Scintillators for the Detection of Neutrinos in Future Large-Scale Detectors,”}}\\
                  & Research Advisor: Prof. Dr. Lothar Oberauer \\
                  & Grade: magna cum laude (with great honors) \vspace{0.35em} \\

10/2015 – 05/2018 &\textbf{Master of Science in Physics} \\
                  & Technische Universit\"at M\"unchen (TUM), Germany \\
                  & Specialization in Nuclear, Particle and Astrophysics, \\
                  & Thesis: \textit{“Spectro-Interferometric Signatures of the Broad Line Regions in Active Galactic Nuclei,”} Research Advisor: Prof. Dr. Jason Dexter \\
                  & Grade: 1.5 (passed with distinction) \vspace{0.22em} \\
09/2016 – 02/2017 & \textbf{ERASMUS+ exchange student} \\
                  & Sorbonne Université, France \\
                  & Nuclei, Particles, Astroparticles and Cosmology (NPAC, Master 2 level) \vspace{0.22em} \\
10/2012 – 09/2015 & \textbf{Bachelor of Science in Physics} \\
                  & Technische Universit\"at M\"unchen (TUM), Germany \\
                  & Grade: 2.6 (passed) \vspace{0.22em} \\
\end{tabular}
\newpage
\begin{tabular}{@{} l p{13cm}}
09/2004 – 06/2012 & \textbf{Abitur} (General Higher Education Entrance Qualification) \\
                  & {Gymnasium Vilshofen}, {Germany}  \\
                  & Grade: 2.5 (passed with merit)  \\
\end{tabular}
\vspace{1em}
\noindent

\cvsection{Professional Activities}\vspace{\cvSectionToTable}
\vspace{0.5em}
\begin{tabular}{@{} l p{12cm}}

	02/2026 – today &  Simulation, development, characterization, and installation of the light calibration systems for the KamLAND2-Zen and DarkSide-20k experiments to improve the detector response and energy scale. \vspace{0.35em}\\

	07/2025 – today & Guest researcher (unpaid), TUM \vspace{0.35em}\\
	05/2019 – 07/2025 & \textbf{PhD Thesis}\\
  	& I study organic and water-based liquid scintillators comprising different solvents and fluors. Using UV light, radioactive sources and particle accelerators
	I characterize liquid scintillators,~e.g., for JUNO and~\textsc{Theia}, concering emission spectra, UV, electron and proton scintillation time profiles, and proton quenching factors with dedicated experiments at room and cold temperatures.
	I thoroughly analyze the large amounts of data and compare them to models, which include numerical convolutions.
	Additionally, I characterized the used photomultiplier tubes~(PMTs) concerning gain voltage dependency at single photoelectron~(SPE) intensity using a picosecond laser system.\vspace{0.35em}\\

	07/2022 – 03/2025 & Laser protection officer of the chair E15, TUM \vspace{0.35em}\\

	09/2020 – 03/2025 & Chemistry laboratory manager of the chair E15, TUM \vspace{0.35em}\\

	21/11/2024 – 01/12/2024 & Active participation in a beamtime at the Heidelberger Ionenstrahl-Therapiezentrum, Heidelberg, Germany \vspace{0.35em}\\

	04/2022 – 02/2023 & JUNO Deputy Young Researcher Representative \vspace{0.35em}\\

	07/03/2022 – 07/14/2022 & Active participation in pumping out the far detector of the Double Chooz experiment, Centrale nucléaire de Chooz, France \vspace{0.35em}\\

	04/22/2022 – 05/12/2022 & Co-leading beamtimes at the CN accelerator and at the Tandem-XTU \\
	& accelerator, INFN LNL, Legnaro, Italy \vspace{0.35em}\\

	12/14/2021 – 12/24/2021 & Co-leading a beamtime at the CN accelerator, INFN LNL, Legnaro, Italy \\
	06/02/2021 – 06/22/2021 & Co-leading a beamtime at the CN accelerator, INFN LNL, Legnaro, Italy \\

	04/12/2021 – 04/23/2021 & Active participation in pumping out the near detector of the Double Chooz experiment, Centrale nucléaire de Chooz, France \vspace{0.35em}\\

	01/18/2021 – 01/30/2021 & Active participation in pumping out the near detector of the Double Chooz experiment, Centrale nucléaire de Chooz, France \vspace{0.35em}\\

	10/09/2019 – 10/11/2019 & Co-organizer of the \textit{“JUNO DFG Meeting 2019,”} {TUM, Germany} \vspace{0.35em}\\

	09/16/2019 – 09/27/2019 & Co-leading a beamtime at the MLL accelerator, Garching, Germany \vspace{0.35em}\\

	07/27/2019 – 08/29/2019 & Expert shifter at the \textit{“PMT Characterization and Instrumentation Station for JUNO,”} Pan-Asia, Zhongshan, China \vspace{0.3em} \\

	04/28/2019 – 05/06/2019 & Co-leading a beamtime at the MLL accelerator, Garching, Germany \vspace{0.35em}\\

	08/12/2018 – 08/16/2018 & Assistence in an observing program with ESO VLTI GRAVITY/AT, \mbox{24 hours in total}, {Paranal Observatory, Chile} \vspace{0.3em} \\

\end{tabular}
\newpage
\begin{tabular}{@{} l p{12cm}}
	05/2017 – 05/2018 & \textbf{Master's Thesis}\\
	& I developed models of the broad line region~(BLR) as a collection of optically thin clouds orbiting the supermassive black hole in an active galactic nucleus~(AGN). Comparing model predictions for spectral lines and differential phases with interferometric~VLTI/GRAVITY data of quasars,~e.g.,~3C~273, or other~AGN, provide constraints on their orientation, structure and dynamics, such as black hole masses,~BLR sizes or inclinations. Markov chain Monte Carlo~(MCMC) methods were used. \\
\end{tabular}\par
\vspace{1em}\par
\cvsection{Professional Affiliations}
\vspace{0.5em}
\begin{tabular}{@{} l p{13cm}}
	02/2026 – present & \href{https://www.awa.tohoku.ac.jp/en/kamland/}{KamLAND collaboration} (international collaboration)\vspace{0.35em} \\
	02/2026 – present & \href{https://darkside.lngs.infn.it/}{DarkSide collaboration} (international collaboration)\vspace{0.35em} \\
	01/2021 – present & \href{http://doublechooz.in2p3.fr/Public/English/Collaboration/collaboration.php}{Double Chooz collaboration} (international collaboration)\vspace{0.35em} \\
	11/2019 – present & \textsc{Theia} collaboration (international collaboration)\vspace{0.35em} \\
	01/2019 – 02/2026 & \href{http://juno.ihep.cas.cn/}{JUNO collaboration} (international collaboration)\vspace{0.35em} \\
	11/2017 – present & \href{https://www.dpg-physik.de/}{German Physical Society (DPG)}\\

\end{tabular}
\vspace{1em}
\cvsection{Teaching Experience and Training}
\vspace{0.5em}
Technische Universit\"at M\"unchen\par\vspace{0.45em}
\begin{tabular}{@{} l p{13cm}}
Winter 2024/2025 & Tutor, Introduction to Nuclear, Particle and Astrophysics\\
& (temporary assistance) \vspace{0.35em}\\

Summer 2024 & Tutor, Physics II for Geodesy and Geo-Information (temporary assistance) \vspace{0.35em}\\

Summer 2022 & Tutor, Particle Oscillations (offline and online) \vspace{0.35em}\\

Summer 2021 & Tutor, Particle Oscillations (online) \vspace{0.35em}\\

Winter 2020/2021 & Tutor, Introduction to Nuclear, Particle and Astrophysics (online) \vspace{0.35em}\\
Summer 2020 & Tutor, Particle Oscillations (online) \vspace{0.35em}\\

Winter 2019/2020 & Tutor, Introduction to Nuclear, Particle and Astrophysics \vspace{0.35em}\\
& Instructor, Physics Lab Course for Food Chemistry \vspace{0.35em}\\
& Tutor, Pre-study Physics course \vspace{0.35em}\\

Summer 2019 & Tutor, Particle Oscillations \\
\end{tabular}
\vspace{1em}
\cvsection{Co-supervision of Students}
\vspace{0.5em}
2 Master and 4 Bachelor students, Technische Universit\"at M\"unchen\par
\vspace{1em}
\cvsection{Languages}
\begin{itemize}
	\item German (native)
	\item English (advanced, TOEFL iBT: 104/120, test made 2018)
	\item French (elementary, A2)
	\item Latin (Latinum)
\end{itemize}
\vspace{1em}
\cvsection{Computer Skills}
\begin{itemize}
	\item \LaTeX, Office programmes
	\item Python, Mathematica, MATLAB, OriginPro, ROOT
	\item Photoshop, GIMP, RAW converters, Inkscape
\end{itemize}
\vspace{1em}
\cvsection{Summer Schools}
\begin{itemize}
	\item July 17 – 21, 2022 - Summer School of the SFB1258 Munich School on Neutrinos and Dark Matter (MONA), Raitenhaslach, Germany
	\item June 20 – 24, 2022 - SOUP2022 – The 2nd INFN School on Underground Physics, Gran Sasso National Laboratory and Gran Sasso Science Institute, Italy
	\item July 12 – 19, 2019 - 19th JINR-ISU Baikal Summer School on Physics of Elementary Particles and Astrophysics, Bolshiye Koty, Russia
	\item July 9 – 14, 2018 - 9th VLTI Summer School 2018, Lisbon, Portugal (with travel grant)
\end{itemize}
\vspace{1.0em}
\cvsection{Invited Conference Presentations, Colloquia and Seminars}

\begin{itemize}
\item December 7, 2023 - Plenary talk: \href{https://indico.cern.ch/event/1303630/contributions/5599770/}{\textit{“Status and Prospects of the JUNO Experiment,”}} \textbf{The 17th International Workshop on Tau Lepton Physics (TAU 2023)}, Louisville, Kentucky, USA

\item February 23, 2023 - \textit{“Liquid Scintillator Characterization Experiments for Particle Identification in JUNO and \textsc{Theia},”} \textbf{ DESY}, Zeuthen, Germany (with travel grant)

\item January 18, 2020 - \textit{“Fluorescence Decay-Time Spectroscopy of the JUNO Liquid Scintillator using Gamma Radiation and a Pulsed Neutron Beam,”} \textbf{INFN Laboratori Nazionali di Legnaro}, Legnaro, Italy
\end{itemize}
\vspace{1.0em}
\cvsection{Contributed Conference Presentations and Posters}
\begin{itemize}
\item March 6, 2024 - \href{https://www.dpg-verhandlungen.de/year/2024/conference/karlsruhe/part/t/session/57/contribution/2}{\textit{“Time Profile Measurements of the Cooled TAO Liquid Scintillator,”}} \textbf{DPG Spring Meeting 2024}, Karlsruhe, Germany (with travel grant)

\item August 30, 2023 - Poster: \href{https://indico.cern.ch/event/1199289/contributions/5445889/}{\textit{Scintillation Time Profiles of Slow Organic and Water-Based Liquid Scintillators using a Pulsed Neutron Beam,”}} \textbf{XVIII International Conference on Topics in Astroparticle and Underground Physics (TAUP 2023)}, Vienna, Austria

\item March 23, 2023 - \href{https://www.dpg-verhandlungen.de/year/2023/conference/smuk/part/t/session/143/contribution/3}{\textit{“Fluorescence Time Profiles of Slow Organic and Water-Based Liquid Scintillators using a Pulsed Neutron Beam,”}} \textbf{DPG Spring Meeting 2023}, Dresden, Germany (with travel grant)

\item July 20, 2022 - Poster: {\textit{“Liquid Scintillator R\&D: Overview of Quenching Factor and Scintillation Time Profile Measurements at INFN Legnaro,”}} MONA Summer School, Raitenhaslach, Germany

\item March 22, 2022 - \href{https://www.dpg-verhandlungen.de/year/2022/conference/heidelberg/part/t/session/48/contribution/9}{\textit{“Fluorescence Time Profiles of the JUNO and TAO Liquid Scintillators using a Pulsed Neutron Beam in the Energy Range from 3.5 to 5.5 MeV,”}} \textbf{DPG Spring Meeting 2022}, Online

\item March 16, 2021 - \href{https://www.dpg-verhandlungen.de/year/2021/conference/dortmund/part/t/session/44/contribution/10}{\textit{“Measuring the Fluorescence Time Profile of the JUNO Scintillator with Gamma and Neutron Excitation,”}} \textbf{DPG Spring Meeting 2021}, Online

\item June 24, 2020 - Poster: \href{https://indico.fnal.gov/event/19348/contributions/186384/}{\textit{“Measuring the Fluorescence Time Profile of the JUNO Liquid Scintillator using Gamma Radiation and a Pulsed Neutron Beam,”}} \textbf{The XXIX International Conference on Neutrino Physics and Astrophysics (Neutrino 2020)}, Online

\item July 17, 2019 - \textit{“Fluorescence Decay Time Measurements of JUNO LS using Gamma Radiation and a Pulsed Neutron Beam,”} \textbf{19th JINR-ISU Baikal Summer School on Physics of Elementary Particles and Astrophysics}, Bolshiye Koty, Russia

\item December 10, 2018 - \href{https://www.torus2018.org/TALKS/18.12.10-S3.3-Stock.pdf}{\textit{“Spectro-Interferometric Signatures of the Broad Line Regions in Active Galactic Nuclei”}}, \textbf{TORUS 2018},
Puerto Varas, Chile (with travel grant)
\item July 10, 2018 - \textit{“Spectro-Interferometric Signatures of the Broad Line Regions in Active Galactic Nuclei,”} \textbf{9th VLTI Summer School 2018}, Lisbon, Portugal (with travel grant)
\end{itemize}
\vspace{1.em}\par

\cvsection{Peer-Reviewed Publications}
2400+ citations \& h-index 22 (\href{https://scholar.google.de/citations?hl=de&user=oXl77gMAAAAJ&view_op=list_works&sortby=pubdate}{Google Scholar}), ORCID: \href{https://orcid.org/0000-0002-5963-7431}{0000-0002-5963-7431},\\  \href{https://inspirehep.net/authors/1880007?ui-citation-summary=true}{INSPIRE},  \href{https://ui.adsabs.harvard.edu/search/filter_author_facet_hier_fq_author=OR&filter_author_facet_hier_fq_author=author_facet_hier%3A%221%2FStock%2C%20M%2FStock%2C%20M%20%20R%22&filter_author_facet_hier_fq_author=author_facet_hier%3A%221%2FStock%2C%20M%2FStock%2C%20Matthias%20Raphael%22&fq=%7B!type%3Daqp%20v%3D%24fq_author%7D&fq_author=(author_facet_hier%3A%221%2FStock%2C%20M%2FStock%2C%20M%20%20R%22%20OR%20author_facet_hier%3A%221%2FStock%2C%20M%2FStock%2C%20Matthias%20Raphael%22)&p_=0&q=%20author%3A%22stock%2C%20m.r.%22&sort=date%20desc%2C%20bibcode%20desc}{ADS}, \href{https://www.researchgate.net/profile/Matthias-Stock-2}{ResearchGate}
\vspace{0.4em}
\begin{etaremune}[leftmargin=1.65em]
\item \textit{“Picosecond laser test unit for photosensor characterization at ambient and low temperatures,”}\\\textbf{M.R. Stock} et al., 2026, \href{https://doi.org/10.1016/j.nima.2026.171476}{Nucl. Instr. and Meth. in Phys. Res. Sec. A 1880, 171476}, \href{https://doi.org/10.48550/arXiv.2512.19667}{arXiv:2512.19667}
\\
\textbf{Corresponding author}

\item \textit{“Design, waterproofing, and mass production of the 3-inch PMT frontend system of JUNO,”} \\ JUNO Collaboration: J. Xu et al., including \textbf{M.R. Stock}, 2026, \\ \href{https://doi.org/10.1016/j.nima.2026.171301}{Nucl. Instr. and Meth. in Phys. Res. Sec. A 1086, 171301}

\item \textit{“Simulation of the Background from~$\ce{^{13}C}(\upalpha, \ce{n}) \ce{^{16}O}$ Reaction in the~JUNO Scintillator,”} \\ JUNO Collaboration: T. Adam et al., including \textbf{M.R. Stock}, 2025, \href{https://doi.org/10.1140/epjc/s10052-025-14333-4}{Eur. Phys. J. C \textbf{85}, 1080}

\item \textit{“PALM - Precision Attenuation Length Measurement in liquid scintillators,”} \\ V. Rompel et al., including \textbf{M.R. Stock}, 2025, \href{https://doi.org/10.1088/1748-0221/20/04/P04019}{JINST \textbf{20} P04019}

\item \textit{“Potential to identify the neutrino mass ordering with reactor antineutrinos in JUNO,”} JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2025, \href{https://doi.org/10.1088/1674-1137/ad7f3e}{Chinese Phys. C \textbf{49} 033104}

\item \textit{“Prediction of energy resolution in the JUNO experiment,”} JUNO Collaboration: \\ A. Abusleme et al., including \textbf{M.R. Stock}, 2025,
\href{https://doi.org/10.1088/1674-1137/ad83aa}{Chinese Phys. C \textbf{49} 013003}

\item \textit{“JUNO sensitivity to invisible decay modes of neutrons,”}, JUNO Collaboration: \\ A. Abusleme et al., including \textbf{M.R. Stock}, 2025, \href{https://doi.org/10.1140/epjc/s10052-024-13638-0}{Eur. Phys. J. C \textbf{85}, 5}

\item \textit{“The design and technology development of the JUNO central detector,”} JUNO Collaboration: \\
A. Abusleme et al., including \textbf{M.R. Stock}, 2024,
\href{https://doi.org/10.1140/epjp/s13360-024-05830-8}{Eur. Phys. J. Plus \textbf{139}, 1128}

\item \textit{“Development of a bi-solvent liquid scintillator with slow light emission,”} \\ H. Th. J. Steiger, \textbf{M.R. Stock} et al.,~2024, \href{https://doi.org/10.1088/1748-0221/19/09/P09015}{JINST \textbf{19} P09015}
\\
\textit{\textbf{Contribution:} Active participation in the beamtimes and performing the data analysis of the emission spectra and scintillaton time profiles}

\item \textit{“Development, characterization and production of a novel water-based liquid scintillator based on the Surfactant TRITON X-100,”} \\ H. Th. J. Steiger, M. Böhles, \textbf{M.R. Stock} et al.,~2024, \href{https://doi.org/10.1088/1748-0221/19/09/P09008}{JINST \textbf{19} P09008}
\\
\textit{\textbf{Contribution:} Active participation in the beamtimes and performing the data analysis of the emission spectra and the scintillaton time profiles}

\item \textit{“Model-independent Approach of the JUNO $\ce{{^8}B}$ Solar Neutrino Program,”} \\ JUNO Collaboration: J.~Zhao et al., including \textbf{M.R. Stock},~2024, \href{https://doi.org/10.3847/1538-4357/ad2bfd}{ApJ \textbf{965} 122}

\item \textit{“Fast neutron production at the LNL Tandem from the $\ce{^{7}Li}(\ce{^{14}N},\ce{xn})\ce{X}$ reaction,”} \\  P. Torres-Sánchez, H. Th. J. Steiger et al., including \textbf{M.R. Stock}, 2024, \href{https://doi.org/10.1140/epjc/s10052-024-12658-0}{Eur. Phys. J. C \textbf{84}, 372},\\
\textit{\textbf{Contribution:} Active participation in the beamtime}

\item \textit{“Real-time monitoring for the next core-collapse supernova in JUNO,”} JUNO Collaboration: \\ A. Abusleme et al., including \textbf{M.R. Stock}, 2024,
\href{https://doi.org/10.1088/1475-7516/2024/01/057}{JCAP 01 (2024) 057}, \href{https://doi.org/10.48550/arXiv.2309.07109}{arXiv.2309.07109}

\item \textit{“JUNO sensitivity to $\ce{^{7}Be}$, pep, and CNO solar neutrinos,”} JUNO Collaboration: \\ A. Abusleme et al., including \textbf{M.R. Stock}, 2023, \href{https://doi.org/10.1088/1475-7516/2023/10/022}{JCAP 10 (2023) 022}, \href{https://doi.org/10.48550/arXiv.2303.03910}{arXiv:2303.03910}

\item \textit{“The JUNO experiment Top Tracker,”} JUNO Collaboration: A. Abusleme et al., \\  including \textbf{M.R. Stock}, 2023, \href{https://doi.org/10.1016/j.nima.2023.168680}{Nucl. Instr. and Meth. in Phys. Res. Sec. A 1057, 168680},  \href{https://doi.org/10.48550/arXiv.2303.05172}{arXiv:2303.05172}

\item \textit{“JUNO sensitivity to the annihilation of MeV dark matter in the galactic halo,”} \\ JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2023, \href{https://doi.org/10.1088/1475-7516/2023/09/001}{JCAP 09 (2023) 001}, \href{https://doi.org/10.48550/arXiv.2306.09567}{arXiv.2306.09567}

\item \textit{“Nuclear physics midterm plan at Legnaro National Laboratories (LNL),”} \\ M. Ballan et al., including \textbf{M.R. Stock}, 2023,   \href{https://doi.org/10.1140/epjp/s13360-023-04249-x}{Eur. Phys. J. Plus \textbf{138}, 709}

\item \textit{“JUNO sensitivity on proton decay $p \rightarrow \bar{\nu} K^+$ searches,”} JUNO Collaboration: \\ A. Abusleme et al., including \textbf{M.R. Stock}, 2023, \href{http://hepnp.ihep.ac.cn/article/id/bcbe9b7d-149c-4146-a08a-8ee6a3949734}{Chinese Phys. C \textbf{47} (10), 1-17}

\item \textit{“Mass testing and characterization of 20-inch PMTs for JUNO,”} JUNO Collaboration: \\ A. Abusleme et al., including \textbf{M.R. Stock}, 2022, \href{https://doi.org/10.1140/epjc/s10052-022-11002-8}{Eur. Phys. J. C \textbf{82}, 1168}

\item \textit{“Sub-percent precision measurement of neutrino oscillation parameters with JUNO,”} \\ JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2022, \\ \href{http://dx.doi.org/10.1088/1674-1137/ac8bc9}{Chinese Phys. C \textbf{46} 123001}

\item \textit{“Prospects for detecting the diffuse supernova neutrino background with JUNO,”} \\ JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2022,\\
\href{https://doi.org/10.1088/1475-7516/2022/10/033}{JCAP 10 (2022) 033}, \href{https://doi.org/10.48550/arXiv.2205.08830}{arXiv:2205.08830v1}

\item \textit{“The Double Chooz antineutrino detectors,”} Double Chooz Collaboration:\\ H.~de Kerret et al., including \textbf{M.R. Stock}, 2022, \href{https://doi.org/10.1140/epjc/s10052-022-10726-x}{Eur. Phys. J. C \textbf{82}, 804}\\ \textit{\textbf{Contribution:} Active participation onsite for measuring the mass of the liquid of the Gamma Catcher of the near detector to derive the proton number}

\item \textit{“Potential for a precision measurement of solar $pp$ neutrinos in the Serappis Experiment,”}\\ L.~Bieger et al., including \textbf{M.R. Stock}, 2022, \href{https://doi.org/10.1140/epjc/s10052-022-10725-y}{Eur. Phys. J. C \textbf{82}, 779}

\item \textit{“Damping signatures at JUNO, a medium-baseline reactor neutrino oscillation experiment,”}\\ JUNO Collaboration: J.~Wang et al., including \textbf{M.R. Stock}, 2022, \href{https://doi.org/10.1007/JHEP06(2022)062}{J. High Energ. Phys. \textbf{2022}, 62}

\item \textit{“Combined sensitivity of JUNO and KM3NeT/ORCA to the neutrino mass ordering,”} \\ KM3NeT Collaboration and JUNO Collaboration Members: S.~Aiello et al.\\  including \textbf{M.R. Stock}, 2022, \href{https://doi.org/10.1007/JHEP03(2022)055}{J. High Energ. Phys. \textbf{2022}, 55}

\item \textit{“JUNO physics and detector,”} JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2022, \href{https://doi.org/10.1016%2Fj.ppnp.2021.103927}{Progress in Particle and Nuclear Physics, 123, 103927}, \href{https://arxiv.org/abs/2104.02565v2}{arXiv:2104.02565v2}

\item \textit{“Radioactivity control strategy for the JUNO detector,”} JUNO Collaboration: \\ A. Abusleme et al., including \textbf{M.R. Stock}, 2021, \href{https://doi.org/10.1007/JHEP11(2021)102}{J. High Energ. Phys. \textbf{2021}, 102}

\item \textit{“The design and sensitivity of JUNO’s scintillator radiopurity pre-detector OSIRIS,”} \\ JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2021, \href{https://doi.org/10.1140/epjc/s10052-021-09544-4}{Eur. Phys. J. C \textbf{81}, 973}

\item \textit{“JUNO sensitivity to low energy atmospheric neutrino spectra,”} JUNO Collaboration: \\ A. Abusleme et al., including \textbf{M.R. Stock}, 2021, \href{https://doi.org/10.1140/epjc/s10052-021-09565-z}{Eur. Phys. J. C \textbf{81}, 887}

\item \textit{“Calibration strategy of the JUNO experiment,”} JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2021, \href{https://doi.org/10.1007/JHEP03(2021)004}{J. High Energ. Phys. \textbf{2021}, 4}

\item \textit{“Feasibility and physics potential of detecting $\ce{^{8}B}$ solar neutrinos at JUNO,”} JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2021, \href{https://doi.org/10.1088/1674-1137/abd92a}{Chinese Phys. C \textbf{45} 023004}

\item \textit{“\textsc{Theia}: an advanced optical neutrino detector,”} M.~Askins et al., including \textbf{M.R. Stock}, 2020,\\ \href{https://link.springer.com/article/10.1140/epjc/s10052-020-7977-8}{Eur. Phys. J. C \textbf{80}, 416}

\item \textit{“Combined sensitivity to the neutrino mass ordering with JUNO, the IceCube Upgrade, and PINGU,”} IceCube-Gen2 Collaboration, and JUNO Collaboration Members: \\ M.~G.~Aartsen et al., including \textbf{M.R. Stock}, 2020, \href{https://doi.org/10.1103/PhysRevD.101.032006}{Phys. Rev. D \textbf{101}, 032006}

\item \textit{“Spatially resolved rotation of the broad-line region of a quasar at sub-parsec scale,”} \\ GRAVITY collaboration: E.~Sturm, J.~Dexter, O.~Pfuhl, \textbf{M.R. Stock} et al., 2018, \\ \href{https://www.nature.com/articles/s41586-018-0731-9}{Nature \textbf{563}, 657–660}, \href{https://arxiv.org/abs/1811.11195v1}{arXiv:1811.11195v1}\\ 
\textit{\textbf{Contribution:} Developed models and fit them to VLTI/GRAVTIY data of the quasar 3C 273 to derive,~e.g., broad-line region size and black hole mass}

\end{etaremune}
\vspace{1em}\par

%\newpage
\cvsection{Peer-Reviewed Conference Proceedings}

\begin{itemize}
	\item {\textit{“Status and Prospects of the~JUNO Experiment,”}} \textbf{M.R. Stock}, \\on behalf of the JUNO Collaboration, 2025, \href{https://doi.org/10.21468/SciPostPhysProc.17.020}{SciPost Phys. Proc. 17, 020}, \href{https://doi.org/10.48550/arXiv.2405.07321}{arXiv:2405.07321}\\
	\textbf{Corresponding author}

	\item {\textit{“Scintillation Time Profiles of Slow Organic and Water-Based Liquid Scintillators using a Pulsed Neutron Beam,”}} \textbf{M.R. Stock} et al., 2024, \href{https://pos.sissa.it/441/287/}{PoS (TAUP2023) 287}\\
	\textbf{Corresponding author}
\end{itemize}
\vspace{1em}\par
\newpage
\cvsection{Selected Unrefereed Publications}
\begin{itemize}
\item \textit{“First measurement of reactor neutrino oscillations at JUNO,”} JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2025,
\href{https://doi.org/10.48550/arXiv.2511.14593}{arXiv:2511.14593}

\item \textit{“Initial performance results of the JUNO detector,”} JUNO Collaboration: A. Abusleme et al., including \textbf{M.R. Stock}, 2025, submitted to Chinese Phys. C, \href{https://doi.org/10.48550/arXiv.2511.14590}{arXiv:2511.14590}

\item \textit{“Prospects for geoneutrino detection with JUNO,”} JUNO Collaboration: T. Adam et al., including \textbf{M.R. Stock}, 2025, \href{https://doi.org/10.48550/arXiv.2511.07227}{arXiv:2511.07227}

\item \textit{“First Measurement of Neutrino Emissions from Spent Nuclear Fuel by the Double Chooz Experiment,”} Double Chooz Collaboration: T. Abrah\~ao et al., including \textbf{M.R. Stock}, 2025, \href{https://doi.org/10.48550/arXiv.2510.04869}{arXiv:2510.04869}

\item \textit{“The Core of the Matter — Spatially Resolving Active Galactic Nuclei with GRAVITY,”} \\ GRAVITY collaboration: E.~Sturm et al., including \textbf{M.R. Stock}, 2022, \\ \href{https://doi.org/10.18727/0722-6691/5275}{ESO The Messenger, 188:20-25}

\item \textit{“\textsc{Theia}: Summary of physics program. Snowmass White Paper Submission,”}  M.~Askins et al., including \textbf{M.R. Stock}, 2022, \href{https://doi.org/10.48550/arXiv.2202.12839}{arXiv:2202.12839v1}

\item \textit{“TAO Conceptual Design Report: A Precision Measurement of the Reactor Antineutrino Spectrum with Sub-percent Energy Resolution,”} JUNO Collaboration: A. Abusleme et al., \\ including \textbf{M.R. Stock}, 2020, \href{https://doi.org/10.48550/arXiv.2005.08745}{arXiv:2005.08745v1}

\item \textit{“Spatially Resolving the Quasar Broad Emission Line Region,”} GRAVITY collaboration: \\ R.~Abuter et al., including \textbf{M.R. Stock}, 2019, \href{https://doi.eso.org/10.18727/0722-6691/5166}{ESO The Messenger, 178:20–24}
\end{itemize}

\end{document}
